---
title: "Time Series Project"
author: ""
date: "2023-11-17"
output: pdf_document
---

```{r message=FALSE, warning=FALSE}
library(fpp3)
library(prophet)
library(fable.prophet)
```

```{r}
insurance |> autoplot(Quotes)+
  labs(y = "Quotes", x = "Month",
       title = "Monthly quotations for a US insurance company from January 2002 to April 2005")

insurance |>
  pivot_longer(c(Quotes, TVadverts), names_to="Series") |>
  autoplot(value)
```
```{r}
insurance |> gg_lag(Quotes, geom='point')
insurance |> ACF(Quotes, lag_max = 12) |> autoplot()
insurance |> PACF(Quotes, lag_max = 12) |> autoplot()
```

```{r}
Train <- insurance[0:32,]
Test <- insurance[33:40,]
```


```{r}
ins_stl <- Train |> 
  model(stl = STL(Quotes))

ins_stl |>
  components() |>
  autoplot()
```


## Fitting Models

```{r fit1}
fit1 <-  Train |>  model(
        lm     =  TSLM(Quotes),
        lm2    =  TSLM(Quotes ~ TVadverts),
        lm3    =  TSLM(Quotes ~ lag(TVadverts)),
        lm4    =  TSLM(Quotes ~ TVadverts + lag(TVadverts)),
        ARIMA  =  ARIMA(Quotes),
        ARIMA2 =  ARIMA(Quotes ~ TVadverts),
        ARIMA3 =  ARIMA(Quotes ~ lag(TVadverts)),
        ARIMA4 =  ARIMA(Quotes ~ TVadverts + lag(TVadverts)),
        Mean   =  MEAN(Quotes),
        SNaive =  SNAIVE(Quotes),
        Naive  =  NAIVE(Quotes),
        Drift  =  RW(Quotes ~ drift()),
        ETS    =  ETS(Quotes),
        NNET   =  NNETAR(Quotes),
        Prophet = prophet(Quotes)
)

acc1 <- accuracy(fit1) |> arrange(RMSE)
acc1

print(c("The best mdoel on Train is: ", acc1$.model[1]))

fit1[,acc1$.model[1]] |>  gg_tsresiduals()

# augment(fit1) |> filter(.model == acc1$.model[1]) |> 
#   features(.resid, ljung_box, lag=12, dof=0)
# 
# augment(fit1) |> filter(.model == acc1$.model[1]) |>
#   features(.innov, box_pierce, lag = 12,  dof = 0)


augment(fit1) |> filter(.model == acc1$.model[1]) |>
  ggplot(aes(x = Month)) +
  geom_line(aes(y = Quotes , colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted"))+
  ggtitle("The best model of training and actual data")

fc1 <- fit1 |> forecast(new_data = Test) 


accT1 <- accuracy(fc1, Test) |> arrange(RMSE)
accT1
print(c("The best mdoel on Test is: ", accT1$.model[1]))


fc1 |> filter(.model == accT1$.model[1]) |> 
  autoplot(Train, level = NULL) +
  labs(y = "Quotes", x = "Month",
  title = "8 months forecast for quotations") +
    autolayer(Test, colour = "darkgray")

```

## Fitting Combination Models

```{r Combination, message=FALSE, warning=FALSE}

fit2 <- fit1 |>  mutate(
    Combination1 = (lm2 + lm4)/2,
    Combination2 = (lm2 + ARIMA2)/2,
    Combination3 = (lm2 + ARIMA4)/2,
    Combination4 = (lm4 + ARIMA2)/2,
    Combination5 = (lm4 + ARIMA4)/2,
    Combination6 = (ARIMA2 + ARIMA4)/2,
    Combination7 = (NNET + ARIMA4)/2,
    Combination8 = (NNET + ARIMA2)/2,
    Combination9 = (NNET + Prophet)/2,
    Combination10 = (ARIMA4 + ARIMA2)/2,
    Combination11 = (ARIMA4 + Prophet)/2,
    Combination12 = (ARIMA2 + Prophet)/2,
  )

acc2 <- accuracy(fit2) |> arrange(RMSE)
acc2
print(c("The best mdoel on Train is: ", acc2$.model[1]))
fit2[,acc1$.model[1]] |> gg_tsresiduals()

augment(fit2) |> filter(.model == acc1$.model[1]) |>
  ggplot(aes(x = Month)) +
  geom_line(aes(y = Quotes , colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted"))+
  ggtitle("The best model of training and actual data")

# augment(fit2) |> filter(.model == acc2$.model[1]) |> 
#   features(.resid, ljung_box, lag=12, dof=0)
# 
# augment(fit2) |> filter(.model == acc2$.model[1]) |>
#   features(.innov, box_pierce, dof = 0, lag = 12)


fc2 <- fit2 |> forecast(new_data =  Test)

accT2 <- accuracy(fc2, Test) |> arrange(RMSE)
accT2
print(c("The best mdoel on Test is: ", accT2$.model[1]))


fc2 |> filter(.model == accT2$.model[1]) |> 
  autoplot(Train, level = NULL) +
  labs(y = "Quotes", x = "Month",
  title = "8 months forecast for quotations") +
    autolayer(Test, colour = "darkgray")

```





## Cross Validation

```{r CrossValidation, message=FALSE, warning=FALSE}
insurance_stretch <- insurance |>
  stretch_tsibble(.init = 5, .step = 1) |>
  filter(.id != max(.id))


fit_cv1 <- insurance_stretch |>
   model(
        lm     =  TSLM(Quotes),
        lm2    =  TSLM(Quotes~ TVadverts),
        lm3    =  TSLM(Quotes~ lag(TVadverts)),
        lm4    =  TSLM(Quotes~ TVadverts + lag(TVadverts)),
        Mean   =  MEAN(Quotes),
        SNaive =  SNAIVE(Quotes),
        Naive  =  NAIVE(Quotes),
        Drift  =  RW(Quotes ~ drift()),
        ETS    =  ETS(Quotes),
        NNET   =  NNETAR(Quotes),
        Prophet = prophet(Quotes)
)

fc_cv1 <- fit_cv1 |>
  forecast(new_data = insurance_stretch , h=8)


# Cross-validated
fc_cv1 |> accuracy(insurance) |> arrange(RMSE)

        # ARIMA  =  ARIMA(Quotes),
        # ARIMA2 =  ARIMA(Quotes~ TVadverts),
        # ARIMA3 =  ARIMA(Quotes~ lag(TVadverts)),
        # ARIMA4 =  ARIMA(Quotes~ TVadverts + lag(TVadverts)),
```



## Bootstapped

```{r, message=FALSE, warning=FALSE}
sim <- ins_stl |>
  generate(new_data = Train, times = 100,
           bootstrap_block_size = 24) |>  select(-.model, -Quotes)


fit3 <-  sim |>  model(
        lm     =  TSLM(.sim),
        lm2    =  TSLM(.sim ~ TVadverts),
        lm3    =  TSLM(.sim ~ lag(TVadverts)),
        lm4    =  TSLM(.sim ~ TVadverts + lag(TVadverts)),
        ARIMA  =  ARIMA(.sim),
        ARIMA2 =  ARIMA(.sim ~ TVadverts),
        ARIMA3 =  ARIMA(.sim ~ lag(TVadverts)),
        ARIMA4 =  ARIMA(.sim ~ TVadverts + lag(TVadverts)),
        Mean   =  MEAN(.sim),
        SNaive =  SNAIVE(.sim),
        Naive  =  NAIVE(.sim),
        Drift  =  RW(.sim ~ drift()),
        ETS    =  ETS(.sim),
        NNET   =  NNETAR(.sim),
        Prophet = prophet(.sim)
)

acc3 <- accuracy(fit3) |> arrange(RMSE)

acc3



fc3 <- fit3 |>filter(.rep == acc3$.rep[1]) |> select(-.rep) |> forecast(new_data = Test) 

names(Test)[names(Test) == "Quotes"] <- ".sim"

accT3 <- accuracy(fc3, Test) |> arrange(RMSE)
accT3
print(c("The best mdoel on Test is: ", accT3$.model[1]))

```

```{r}
insurance_stretch <- insurance |>
  stretch_tsibble(.init = 5, .step = 1) |>
  filter(.id != max(.id))

fitCV <- insurance_stretch |>
  model(
        TSLM2    =  TSLM(Quotes~ TVadverts),
        TSLM4    =  TSLM(Quotes~ TVadverts + lag(TVadverts))
  ) |>
  mutate(combination = (TSLM2 + TSLM4) / 2)

fcCV <- fitCV |>
  forecast(new_data = insurance_stretch , h=8)

 fcCV |> filter(.model == "combination") |> accuracy(Test) |> arrange(RMSE)
```

#sign Correlation function 

```{r}
rho.cal<-function(X){
rho.hat<-cor(sign(X-mean(X)), X-mean(X))
return(rho.hat)
}


```

# The sign correlation for the volatility of Quotes indicates that it follows a  distribution is close to normal distribution normal (65,25) based on the table 
```{r}
v <- insurance$Quotes

#volatility
v_new = abs(sqrt(v)-mean(sqrt(v)))
rho.cal(v_new) # find the distribution


#data <- ts(v) %>% as_tsibble()
# create Quarterly data
data <- ts(v_new)%>% as_tsibble()

```
#Applying Neural Network Model to Quotes volatility data 
```{r}
trainNN<- data[0:32,]
testNN<- data[33:40,]


fitNN <-  trainNN %>%
  model(NNETAR(value))
fitNN


```
#volatility forecast for 7 month ahead based on test data
```{r}

fcNN<- fitNN %>%  
  forecast(h = 7) 


```
#volatility forecast plot and 95% confidence interval of volatility  for each year 

```{r}

fcNN%>% autoplot(data) +
 labs(
    y = "Volatility",
    x = "Month",
    title = "NNETAR volatility Forecasts for Quotes"
  )

accuracy(fcNN,testNN)

fcNN%>%hilo(95)



```






